---
title: "COVID-19 analysis report"
author: "Ostap Romanchak, Madiyar Seidaly, Wing Lun Lim, Emily Chiu"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include = FALSE}

# GLOBAL KNITR OPTIONS----
knitr::opts_chunk$set(echo = FALSE, #hide R source codes
                      warning = FALSE, #to not print warnings from R
                      messages = FALSE, #to not print messsges from R
                      include = FALSE, #hide outputs
                      fig.align='center') #align figures at the centre

# ____________________----

```

## Introduction

Through COVID-19 model data of 82,101 cases between 27/12/2019 and 27/07/2019, we investigated the effect of age and gender on mortality and the severity of different symptoms.

## Figures

```{r import Ostap}
# Imported Ostap's script
source("scripts/Ostap.R")

```

```{r plot Ostap, include = TRUE, fig.width = 7, out.height="30%"}
plot(age_death_bar_plot) # Included command to display the plot

```

**Figure 1.** Mortality rate increases with age, with most deaths seen in the age category of over 80 years old.

```{r import Wing}
# Imported Wing's script
source("scripts/Wing.R")

```

```{r plot Wing, include = TRUE, fig.width = 7, out.height="27%"}
plot(gender_death_bar_plot) # Included command to display the plot

```

**Figure 2.** COVID-19 has a male bias in mortality despite less males were sampled (38,376 males and 43,279 females). In the 1338 deaths, 633 were females and 705 were males.

```{r import Madiyar}
# Imported Madiyar's Script
source("scripts/Madiyar.R")

```

```{r plot Madiyar, include = TRUE, fig.width=20, fig.height = 7}
plot(plot_F) # Included command to display the plot

```

**Figure 3.** The different symptoms associated with COVID-19 vary in prevalence among cases where individuals were and were not hospitalized. Sore throat was the least prevalent in both groups. Coughing was the most prevalent among those hospitalized both as an individual symptom and as a collective of symptoms. The loss of taste and smell was the individual most prevalent symptom among those who weren't hospitalized. Headache was the most prevalent collectively along with other symptoms.

```{r import Emily}
# Imported Emily's Script
source("scripts/Emily.R")

```

```{r plot Emily, include = TRUE, fig.width = 7, out.height="28%"}
plot(headache_bar) # Included command to display the plot

```

**Figure 4.** The symptom of headache does not indicate a positive COVID-19 diagnosis. Only 26% of the people with COVID-19 experienced  headache(s), 33% did not, and the status for the remainder could not be confirmed, thus suggesting there is no positive correlation.  

## Conclusion

Human demographics have been shown to influence the mortality and prevalence of various COVID-19 symptoms. Consideration of different demographics and awareness of symptoms will be important in future global responses to worldwide diseases.